Fixed-Parameter Tractable Sampling for RNA Design with Multiple Target Structures

### 2018-05-23 RNARedPrint-Bioinfo2018.tex
update finished benchmarks
Added figure

@@

For a multi-target design instance, individual reasonable target
energies are estimated from averaging the energy over samples at
relatively high weights $e^{\beta}$, setting the targeted \GCb\%
to 60\%. For each instance of the \Software{Modena}
benchmark~\citep{Taneda2015}, we estimated such target energies and
subsequently generated $1\,000$ seed sequences at these energies.
Our procedure is tailored to produce sequences with similar Turner
energy that favor the stability of the target structures having
moderate \GCb\%; all these properties are desirable objectives
for RNA design.  All sampled sequences are evaluated under the
multi-stable design objective function of \citet{Hammer2017}:
% \begin{align}
%   f(S)= \quad & \frac{1}{k} \sum_{\ell=1}^{k} (E(S, R_\ell) - G(S))\notag\\
%    & +\ \xi \frac{2}{k(k-1)} \sum\limits_{1\leq\ell<j\leq k}|E(S,R_\ell) - E(S,R_j)|.
% \end{align}
\begin{align}
  \label{eq:blueprintobjective}
    f(S)= \quad & \frac{1}{k} \sum_{\ell=1}^{k} (E(S, R_\ell) - G(S))\notag\\
   & +\ 0.5\frac{1}{\binom{k}{2}} \sum\limits_{1\leq\ell<j\leq k}|E(S,R_\ell) - E(S,R_j)|.
\end{align}

@@

\begin{table}[t]
\centering
\medskip
\begin{tabular}{@{}>{\bf}l@{\quad}>{\tt}l@{\quad}@{\quad}c@{\quad}c@{\quad}c@{}}
  &   \textbf{\textrm{Dataset}}   & {\bfseries\ourprog{}} & \textbf{Uniform} & \textbf{$\Delta$-Improvement}\\
  Seeds      & 2str & 21.69 ($\pm$4.37) & 37.74 ($\pm$6.45) & 16.05\\
             & 3str & 18.10 ($\pm$3.98) & 30.49 ($\pm$5.41) & 12.39\\
             & 4str & 20.15 ($\pm$3.83) & 32.32 ($\pm$5.23) & 12.17\\
             \cline{2-5}
             & PK60 & 12.12 ($\pm$3.04) & 19.81 ($\pm$4.24) & 7.69\\
             & PK80 & 13.81 ($\pm$3.63) & 24.05 ($\pm$4.93) & 10.24\\
             & LE80 & 10.54 ($\pm$2.77) & 17.80 ($\pm$4.17) & 7.26\\
             \midrule

>>>>

\newcommand{\Obj}{\text{\sf \relsize{-1}MultiDefect}}

@@

To that purpose, we rely on a multi-stable design objective function introduced by \citet{Hammer2017}, named \Obj in the following:
% \begin{align}
%   f(S)= \quad & \frac{1}{k} \sum_{\ell=1}^{k} (E(S, R_\ell) - G(S))\notag\\
%    & +\ \xi \frac{2}{k(k-1)} \sum\limits_{1\leq\ell<j\leq k}|E(S,R_\ell) - E(S,R_j)|.
% \end{align}
\begin{align}
  \label{eq:blueprintobjective}
    \Obj(S)= \quad & \frac{1}{k} \sum_{\ell=1}^{k} (E(S, R_\ell) - G(S))\notag\\
   & +\ 0.5\frac{1}{\binom{k}{2}} \sum\limits_{1\leq\ell<j\leq k}|E(S,R_\ell) - E(S,R_j)|.
\end{align}

For a multi-target design instance, individual reasonable target
energies are estimated from averaging the energy over samples at
relatively high weights $e^{\beta}$, setting the targeted \GCb\%
to 60\%. For each instance of the \Software{Modena}
benchmark~\citep{Taneda2015}, we estimated such target energies and
subsequently generated $1\,000$ seed sequences at these energies.
Our procedure is tailored to produce sequences with similar Turner
energy that favor the stability of the target structures having
moderate \GCb\%; all these properties are desirable objectives
for RNA design.

@@

\begin{table}[t]
\centering
\medskip
\begin{tabular}{@{}>{\bf}l@{\quad}>{\tt}l@{\quad}@{\quad}c@{\quad}c@{\quad}c@{}}
  &   \textbf{\textrm{Dataset}}   & {\bfseries\ourprog{}} & \textbf{\RNAblueprint} & \textbf{$\Delta$-Improvement}\\ \toprule
  Seeds      & 2str & 21.69 ($\pm$4.37) & 37.74 ($\pm$6.45) & 16.05\\
             & 3str & 18.10 ($\pm$3.98) & 30.49 ($\pm$5.41) & 12.39\\
             & 4str & 20.15 ($\pm$3.83) & 32.32 ($\pm$5.23) & 12.17\\
             \cline{2-5}
             & PK60 & 12.12 ($\pm$3.04) & 19.81 ($\pm$4.24) & 7.69\\
             & PK80 & 13.81 ($\pm$3.63) & 24.05 ($\pm$4.93) & 10.24\\
             & LE80 & 10.54 ($\pm$2.77) & 17.80 ($\pm$4.17) & 7.26\\
             \midrule
